### 2015-07-07 paper.tex
change the CD.png

		In recent years, liquid-scintillator detector has played a important role in low-energy
		neutrion physics experiments \cite{lab2, lab3, lab4, lab5, lab6, lab7}.
		JUNO central detector with 35.4m diameter spherical liquid scintillator is the largest
		liquid scintillator detector currently in the world.

@@

		\section{JUNO detector scheme}
		The JUNO detector is composed of a central detector, a water
		cherenkov detector and a muon tracker(shown in Fig.1).The 
		central detector is a LS detector of 20kton fiducial mass and
		3\%/$\sqrt{E(MeV)}$ energy resolution.The central detector is
		submerged in a water pool to be shielded from natural 
		radioactivities from the surrounding rock and air.The water pool
		is equipped with PMTs to detect the cherenkov light from muons.
		On top of the water pool, there is a another muon detector to 
		accurately measure the muon track.
		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{CD.png}
			\figcaption{\label{fig2}   Acrylic option }
		\end{center}

>>>>

		In recent years, liquid-scintillator detector has played a important role in low-energy
		neutrion physics experiments \cite{lab2, lab3, lab4, lab5, lab6, lab7}.
		JUNO central detector with 35.4m diameter  is the largest
		liquid scintillator detector currently in the world.

@@

		\section{JUNO detector scheme}
		The JUNO detector is composed of a central detector, a water
		cherenkov detector and a muon tracker(shown in Fig.1).The 
		central detector is a LS detector of 20kton fiducial mass and
		3\%/$\sqrt{E(MeV)}$ energy resolution.The central detector is
		submerged in a water pool to be shielded from natural 
		radioactivities from the surrounding rock and air.The water pool
		is equipped with PMTs to detect the cherenkov light from muons.
		On top of the water pool, there is a another muon detector to 
		accurately measure the muon track.
		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{CD.png}
			\figcaption{\label{fig2}   Schematic view of the JUNO detector}
		\end{center}
